The \dealii Library, Version 9.5

### 2023-05-22 9.5/paper.tex
Talk about the callback thing.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Uniform structure of callbacks}\label{sec:callbacks}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Uniform error reporting in callbacks}\label{sec:callbacks}

With the current release, \dealii{} has gained interfaces to several
external packages that are largely driven via \textit{callbacks} --
see for example the code example in Section~\ref{sec:trilinos} on how
NOX gains information about the residual vector, how it indicates to
user code that the Jacobian matrix needs to be rebuilt,
and how to solve linearized systems of equations as the sub-steps of
solving a nonlinear problem. Indeed, the interfaces to the nonlinear
solver KINSOL (as part of SUNDIALS) and SNES (as part of PETSc, see
Section~\ref{sec:petsc} function in exactly the same way; the
ODE solver interfaces to ARKode and IDA (also part of SUNDIALS) and TS
(as part of PETSc) also use this style.

This substantially enlarged use of callbacks used by different backend
libraries raises the issue that each underlying package has its own
convention on how success or error codes of these callbacks should be
encoded. In the case of PETSc's SNES and TS, and for Trilinos's NOX,
success is indicated by a zero integer return value, whereas failure is
indicated by a nonzero return value. On the other hand, the SUNDIALS
packages indicate success by a zero integer return value, a
recoverable failure with a positive value, and an irrecoverable failure
with a negative value. Neither of these conventions mesh well with C++
where error codes are generally indicated via exceptions.
It is conceivable that libraries we want to
interface with in the future use yet other conventions.

In order to shield those who write these callbacks from having to
learn the intricacies of the underlying libraries, we have adopted a
convention whereby user-provided callbacks are just regular functions
that return errors via exception as is common in C++. Internally, the
interfaces to different underlying libraries then translate these
exceptions into the appropriate error codes, saving the thrown exception for possible
later use; if an underlying library supports
recoverable errors, then a callback should indicate such an error by
throwing an object of the special type
\texttt{RecoverableUserCallbackError}. If one of the underlying
packages returns with an error caused by a user-provided callback
throwing an exception, then the wrapper code re-throws the previously
saved exception, allowing the calling site to catch it to obtain information
about what might have gone wrong.

This convention for user callbacks is documented in the glossary.
